A weighted sampling algorithm for the design of RNA sequences with targeted secondary structure and nucleotides distribution

### 2013-03-11 ISMB/results_ISMB.tex
eq

\subsection{Design}
 To benchmark our method, we first started by sampling about $100$ sequences per structure. After correcting the free nucleotides with
 \texttt{RNAinverse} we computed their MFE with \texttt{RNAfold} from the \textit{Vienna Package 2.0}~\cite{Hofacker:1994}.

@@

A desirable feature in sequence design, is to produce samples with a high
diversity. Figure~\ref{fig:nb_sols_entropy} shows the number of correct
solutions as their average entropy and base pair entropy, since 
\ourprog  only influences the distribution of nucleotides inside 
stacked base pairs. The most constraining factor for generating valid
 solutions seems to be  low \GCContent and the percentage of free nucleotides.

>>>>

\subsection{Design}
 To benchmark our method, we first started by sampling about $100$ sequences per structure. After correcting the free nucleotides with
 \RNAinverse we computed their MFE with \rnafold from the \textit{Vienna Package 2.0} by~\cite{Hofacker:1994}.

@@

A desirable feature in sequence design, is to produce samples with a high
diversity but with a conserved structure.
Two useful measures are the entropy~\ref{eq:entropy} and the base pair entropy~\ref{eq:bpentropy}.
The entropy is defined as:
\begin{equation}
  \sum_{\substack{i\\b \in (A,C,G,U)}} -p^b_i\log_4 p^b_i
  \label{eq:entropy}
\end{equation}
where $p^b_i$ is the proportion of nucleotides $b$ at position $i$.
The base pair entropy is defined as:
\begin{equation}
  \sum_{i<j}-p_{i,j}\log_2 p_{i,j}
  \label{eq:bpentropy}
\end{equation}
where $p_{i,j}$ is the probability of having a base pair between positions $i$ and $j$. The base pair entropy reflects
the distribution of structures weights in the Boltzmann ensemble. Thus, a low base pair entropy implies a highly conserved structure.
To compute the base pairs probabilities, we used \rnafold from the \texttt{Vienna Package 2.0} developed by~\cite{Hofacker:1994}.

  Figure~\ref{fig:nb_sols_entropy} shows the number of correct
solutions as their average entropy and base pair entropy, since 
\ourprog  only influences the distribution of nucleotides inside 
stacked base pairs. The most constraining factor for generating valid
 solutions seems to be  low \GCContent and the percentage of free nucleotides.
